Field work 2016

### 2017-02-20 analysis/geo2.Rmd
add data reprojected

```{r pacakges}
library('rgdal')
library("leaflet") 
library("sp")
library("raster")
library('dplyr')
library('ggplot2')
```

@@

# field woek points 
fw <- readOGR(paste0(di, 'data_raw/geoinfo/'), layer = 'dendro_garmin', verbose = FALSE)

@@

mymap %>% 
  fitBounds(myext@xmin, myext@ymin, myext@xmax, myext@ymax) %>% 
  addPolylines(data=mig_forest_sj, color='blue', group='Migrame', popup=mig_forest_sj$nombre) %>% 
  addCircles(ots_phe, 
             lng=coordinates(ots_phe)[,'x'], 
             lat=coordinates(ots_phe)[,'y'], 
             group='OBSNEV Fen', radius=2, color = 'red', popup=ots_phe$name) %>% 
  addCircles(ots_gea, 
             lng=coordinates(ots_gea)[,'x'], 
             lat=coordinates(ots_gea)[,'y'], 
             group='Gea Izquierdo 2014', radius=2, color = 'green', popup=ots_gea$name) %>% 
  addCircles(fw, 
             lng=coordinates(fw)[,'coords.x1'], 
             lat=coordinates(fw)[,'coords.x2'], 
             group='Field Work 2016', radius=2, color = 'yellow', popup=fw$name)

@@

mymap %>% 
  fitBounds(myext@xmin, myext@ymin, myext@xmax, myext@ymax) %>% 
  addPolylines(data=mig_forest_ca, color='blue', group='Migrame', popup=mig_forest_ca$nombre) %>% 
  addCircles(ots_phe, 
             lng=coordinates(ots_phe)[,'x'], 
             lat=coordinates(ots_phe)[,'y'], 
             group='OBSNEV Fen', radius=2, color = 'red', popup=ots_phe$name) %>% 
  addCircles(ots_gea, 
             lng=coordinates(ots_gea)[,'x'], 
             lat=coordinates(ots_gea)[,'y'], 
             group='Gea Izquierdo 2014', radius=2, color = 'green', popup=ots_gea$name) %>% 
  addCircles(fw, 
             lng=coordinates(fw)[,'coords.x1'], 
             lat=coordinates(fw)[,'coords.x2'], 
             group='Field Work 2016', radius=2, color = 'yellow', popup=fw$name)
```

>>>>

```{r pacakges}
library('rgdal')
library("leaflet") 
library("sp")
library("raster")
library("tidyverse")
```

@@

# field wok points 
fw <- readOGR(paste0(di, 'data_raw/geoinfo/'), layer = 'dendro_garmin', verbose = FALSE)

mygpx <- paste0(di, 'data_raw/geoinfo/points_dendro_rep.GPX')
my_points <- readOGR(mygpx, layer = 'waypoints', verbose = TRUE)

@@

mymap %>% 
  fitBounds(myext@xmin, myext@ymin, myext@xmax, myext@ymax) %>% 
  addPolylines(data=mig_forest_sj, color='blue', group='Migrame', popup=mig_forest_sj$nombre) %>% 
  addCircles(ots_phe, 
             lng=coordinates(ots_phe)[,'x'], 
             lat=coordinates(ots_phe)[,'y'], 
             group='OBSNEV Fen', radius=2, color = 'red', popup=ots_phe$name) %>% 
  addCircles(ots_gea, 
             lng=coordinates(ots_gea)[,'x'], 
             lat=coordinates(ots_gea)[,'y'], 
             group='Gea Izquierdo 2014', radius=2, color = 'green', popup=ots_gea$name) %>% 
  addCircles(fw, 
             lng=coordinates(fw)[,'coords.x1'], 
             lat=coordinates(fw)[,'coords.x2'], 
             group='Field Work 2016', radius=2, color = 'yellow', popup=fw$name) %>% 
   addCircles(my_points, 
             lng=coordinates(my_points)[,'coords.x1'], 
             lat=coordinates(my_points)[,'coords.x2'], 
             group='Field Work rep ', radius=2, color = 'purple', popup=my_points$name)

@@

mymap %>% 
  fitBounds(myext@xmin, myext@ymin, myext@xmax, myext@ymax) %>% 
  addPolylines(data=mig_forest_ca, color='blue', group='Migrame', popup=mig_forest_ca$nombre) %>% 
  addCircles(ots_phe, 
             lng=coordinates(ots_phe)[,'x'], 
             lat=coordinates(ots_phe)[,'y'], 
             group='OBSNEV Fen', radius=2, color = 'red', popup=ots_phe$name) %>% 
  addCircles(ots_gea, 
             lng=coordinates(ots_gea)[,'x'], 
             lat=coordinates(ots_gea)[,'y'], 
             group='Gea Izquierdo 2014', radius=2, color = 'green', popup=ots_gea$name) %>% 
  addCircles(fw, 
             lng=coordinates(fw)[,'coords.x1'], 
             lat=coordinates(fw)[,'coords.x2'], 
             group='Field Work 2016', radius=2, color = 'yellow', popup=fw$name) %>% 
     addCircles(my_points, 
             lng=coordinates(my_points)[,'coords.x1'], 
             lat=coordinates(my_points)[,'coords.x2'], 
             group='Field Work rep ', radius=2, color = 'purple', popup=my_points$name)
